---
title: "Report Data Collection"
description: |
 This report contains a description of the data entered at the Nigeria pilot sites
author:
  - name: Travis Sondgerath
date: '`r Sys.Date()`'
output:
  html_document:
    # toc: true
    # toc_depth: 2
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F,
                      message = F,
                      warning = F,
                      results = "asis")

library(dplyr)
library(shiny)
library(shinyWidgets)
library(DT)
library(tibble)
library(lubridate)
library(rmarkdown)
library(leaflet)
library(tidyr)
library(ggplot2)
library(stringr)
library(gt)
library(readr)
library(shinydashboard)
library(dashboardthemes)
library(shinyWidgets)
library(plotly)
library(dashboardthemes)

```

# Introduction

This report describes data entered at pilot sites in Nigeria. This report will server to summarize information collected using the [New Registration Form](https://enketo.ona.io/x/YwD9uv2j).

# Summary

Eventually this report should be edited to show just the current state of the data. 

```{r}

equip_info_historical <- read_csv(file = "https://ona.io/pacafenet/99874/460026/download.csv?data-type=dataset",
                                  na = c("n/a", "")) %>%  
  rename(latitude = `_equip_location_latitude`,
         longitude = `_equip_location_longitude`,
         submission_time = "_submission_time",
         submitted_by = "_submitted_by") %>% 
  rename_all(~gsub(pattern = "-", replacement = "_", x = .)) %>% 
  filter(submitted_by != "pacafenet" |
           is.na(submitted_by)) %>% 
  select(equip_id, manufacturer, facility, equip_type, equip_type_other, lab_level, lab_level_is_other, ownership_type, ownership_type_is_other,
         waranty_status, equipment_status, equipment_purchase_status, manual_availability, manufacture_date, freq_service_maintenance, freq_calibration,
         date_active, engineering_service_provider, engineering_service_provider_email_address, most_recent_calibration, most_recent_maintenance,
         latitude, longitude, submitted_by, submission_time) %>% 
  arrange(equip_id, desc(submission_time)) %>%  
  group_by(equip_id) %>% 
  # These if else's seem to account for when things are left blank, good idea, think all are required right now
  mutate(manufacturer = if_else(condition = is.na(manufacturer),
                                true = lead(manufacturer),
                                false = manufacturer),
         facility = if_else(condition = is.na(facility),
                            true = lead(facility),
                            false = facility),
         equip_type = if_else(condition = is.na(equip_type),
                              true = lead(equip_type),
                              false = equip_type),
         equip_type_other = if_else(condition = is.na(equip_type_other),
                                    true = lead(equip_type_other),
                                    false = equip_type_other),
         lab_level = if_else(condition = is.na(lab_level),
                             true = lead(lab_level),
                             false = lab_level),
         lab_level_is_other = if_else(condition = is.na(lab_level_is_other),
                                      true = lead(lab_level_is_other),
                                      false = lab_level_is_other),
         ownership_type = if_else(condition = is.na(ownership_type),
                                  true = lead(ownership_type),
                                  false = ownership_type),
         ownership_type_is_other = if_else(condition = is.na(ownership_type_is_other),
                                           true = lead(ownership_type_is_other),
                                           false = ownership_type_is_other),
         waranty_status = if_else(condition = is.na(waranty_status),
                                  true = lead(waranty_status),
                                  false = waranty_status),
         equipment_status = if_else(condition = is.na(equipment_status),
                                    true = lead(equipment_status),
                                    false = equipment_status),
         equipment_purchase_status = if_else(condition = is.na(equipment_purchase_status),
                                             true = lead(equipment_purchase_status),
                                             false = equipment_purchase_status),
         manual_availability = if_else(condition = is.na(manual_availability),
                                       true = lead(manual_availability),
                                       false = manual_availability),
         manufacture_date = if_else(condition = is.na(manufacture_date),
                                    true = lead(manufacture_date),
                                    false = manufacture_date),
         freq_service_maintenance = if_else(condition = is.na(freq_service_maintenance),
                                            true = lead(freq_service_maintenance),
                                            false = freq_service_maintenance),
         freq_calibration = if_else(condition = is.na(freq_calibration),
                                    true = lead(freq_calibration),
                                    false = freq_calibration),
         date_active = if_else(condition = is.na(date_active),
                               true = lead(date_active),
                               false = date_active),
         engineering_service_provider = if_else(condition = is.na(engineering_service_provider),
                                                true = lead(engineering_service_provider),
                                                false = engineering_service_provider),
         engineering_service_provider_email_address = if_else(condition = is.na(engineering_service_provider_email_address),
                                                              true = lead(engineering_service_provider_email_address),
                                                              false = engineering_service_provider_email_address),
         most_recent_calibration = if_else(condition = is.na(most_recent_calibration),
                                           true = lead(most_recent_calibration),
                                           false = most_recent_calibration),
         most_recent_maintenance = if_else(condition = is.na(most_recent_maintenance),
                                           true = lead(most_recent_maintenance),
                                           false = most_recent_maintenance),
         latitude = if_else(condition = is.na(latitude),
                            true = lead(latitude),
                            false = latitude),
         longitude = if_else(condition = is.na(longitude),
                             true = lead(longitude),
                             false = longitude),
         submitted_by = if_else(condition = is.na(submitted_by),
                                true = lead(submitted_by),
                                false = submitted_by)) 

```



There have been `r length(unique(equip_info_historical$equip_id))` unique pieces of equipment added so far. Below is a brief summary of the data collected so far.


```{r}

# How many unique pieces of equipment



# Looping through descriptive charts

col_list <- colnames(equip_info_historical)[-1]

for(i in col_list){
  
  # For testing
  
  # i <- "manufacturer"  # Counts/pct
  # i <- "manufacture_date"  # Date range - this one is length 0
  # i <- "freq_service_maintenance"
  
  # i <- "freq_service_maintenance"  # Continuous number
  
  # Counts
  
  if(i %in% c("manufactures", "facility", "equip_type", "equip_type_other", "lab_level", "lab_level_is_other", "ownership_type", 
              "ownership_type_is_other", "waranty_status", "equipment_status", "equipment_purchase_status", "manual_availability",  
              "engineering_service_provider", "engineering_service_provider_email_address")){
    
    count_data <- equip_info_historical %>% 
      group_by_at(i) %>% 
      tally() %>% 
      rename_all(~str_to_title(string = str_replace_all(string = ., pattern = "_" , replacement = " "))) %>% 
      mutate(pct = N/sum(.$N)) %>% 
      add_row(N = sum(.$N, na.rm = T),
              pct = 1)
    
    count_data[nrow(count_data), 1] <- "Total"
    
    count_chart <- count_data %>% 
      gt() %>% 
      cols_align(align = "center") %>%
      cols_align(align = "right",
                 columns = vars(N, pct)) %>%
      cols_label(N = "Count") %>%
      fmt_percent(columns = vars(pct), 
                  decimals = 0) %>%
      tab_header(title = paste(str_to_title(string = str_replace_all(string = i, pattern = "_" , replacement = " ")), "Count")) %>%
      tab_options(row.striping.include_stub = T,
                  row.striping.include_table_body = T,
                  table.border.top.color = "black",
                  table_body.border.bottom.color = "black",
                  table.width = "80%")
    
    print(count_chart)
    
  }
  
  # Dates/Numbers
  
  if(i %in% c("freq_service_maintenance", "freq_calibration")){
    
    rows_not_na <- equip_info_historical %>% 
      filter_at(vars(i), all_vars(!is.na(.)))
    
    if(nrow(rows_not_na) == 0){
      
      print(paste("No Data Entered for", str_to_title(string = str_replace_all(string = i, pattern = "_" , replacement = " "))))
      
      next
      
    }
    
    number_chart <- tibble(
      min = round(min(equip_info_historical[i], na.rm = T), digits = 0),
      max = round(max(equip_info_historical[i], na.rm = T), digits = 0),
      avg = round(mean(equip_info_historical[[i]], na.rm = T), digits = 0),
      med = round(median(equip_info_historical[[i]], na.rm = T), digits = 0)
    ) %>% 
      gt() %>%
      cols_align(align = "right") %>%
      cols_label(min = "Min",
                 max = "Max",
                 avg = "Average",
                 med = "Median") %>%
      fmt_number(columns = vars(min, max, avg, med),
                 decimals = 0) %>%
      tab_header(title = paste(str_to_title(string = str_replace_all(string = i, pattern = "_" , replacement = " ")), "Summary")) %>%
      tab_options(row.striping.include_stub = T,
                  row.striping.include_table_body = T,
                  table.border.top.color = "black",
                  table_body.border.bottom.color = "black",
                  table.width = "80%")
    
    print(number_chart)
    
  }
  
  # Dates
  
  if(i %in% c("manufacture_date", "date_active", "most_recent_calibration", "most_recent_maintenance")){

    rows_not_na <- equip_info_historical %>%
      filter_at(vars(i), all_vars(!is.na(.)))

    if(nrow(rows_not_na) == 0){

      cat(paste("No Data Entered for", str_to_title(string = str_replace_all(string = i, pattern = "_" , replacement = " "))))
      
      next

    }

    date_chart <- tibble(
      min = as.character(summary(equip_info_historical[[i]])[[1]]),
      max = as.character(summary(equip_info_historical[[i]])[[6]]),
      avg = as.character(summary(equip_info_historical[[i]])[[4]]),
      med = as.character(summary(equip_info_historical[[i]])[[3]])
    ) %>%
      gt() %>%
      cols_align(align = "center") %>%
      cols_label(min = "Min",
                 max = "Max",
                 avg = "Average",
                 med = "Median") %>%
      fmt_date(columns = vars(min, max, avg, med),
               date_style = 5) %>%
      tab_header(title = paste(str_to_title(string = str_replace_all(string = i, pattern = "_" , replacement = " ")), "Summary")) %>%
      tab_options(row.striping.include_stub = T,
                  row.striping.include_table_body = T,
                  table.border.top.color = "black",
                  table_body.border.bottom.color = "black",
                  table.width = "80%")

    print(date_chart)
    
  }
  
}

# Count by manufactures
  # See if typos possible
  # May want to upcase

# Count by facility
  # Same as above

# Count by equip type

# Count by other
  # consider adding more to the list?

# Also count by lab_level lab_level_is_other ownership_type ownership_type_is_other waranty_status equipment_status equipment_purchase_status manual_availability, engineering_service_provider engineering_service_provider_email_address

# Range of manufacture_date, freq_service_maintenance, freq_calibration, date_active,most_recent_calibration most_recent_maintenance

# ^^^ Should be done in a loop

```






